Detecting Photo Manipulation using Reflections on Curved Surfaces

### 2014-02-17 paper/main.tex
finished future work section

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{1b-genuine}
                \caption{Original}
    \end{subfigure}

    \begin{tabular}{c c}
	    \begin{subfigure}{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-lateral}
	                \caption{Movement about the sphere\\}
	                \label{subfig:1b-lateral}
	    \end{subfigure}
	    &
	    \begin{subfigure}{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-lateral-reflection}
	                \caption{Movement about the sphere, with reflection also moved}
	                \label{subfig:1b-lateral-reflection}
	    \end{subfigure}
	    \\ \\
	    \begin{subfigure}[b]{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-away}
	                \caption{Movement away from the sphere\\}
	                \label{subfig:1b-away}
	    \end{subfigure}
	    &
	    \begin{subfigure}[b]{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-away2}
	                \caption{Movement farther away from the sphere}
	                \label{subfig:1b-away2}
	    \end{subfigure}
    \end{tabular}

    \begin{subfigure}{0.5\textwidth}
                \includegraphics[width=\textwidth]{1b-composite}
                \caption{The reflection is replaced with a reflection from another image (with a smaller sphere)}
                \label{subfig:1b-composite}
    \end{subfigure}
    \caption{A comparison of different types of forgeries in which the green cube is manipulated.}
	\label{forgery-comparison}
\end{figure}

@@

>>>>

\begin{figure}
	\centering
    \begin{tabular}{c c}
	    \begin{subfigure}{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-lateral}
	                \caption{Movement about the sphere\\}
	                \label{subfig:1b-lateral}
	    \end{subfigure}
	    &
	    \begin{subfigure}{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-lateral-reflection}
	                \caption{Movement about the sphere, with reflection also moved}
	                \label{subfig:1b-lateral-reflection}
	    \end{subfigure}
	    \\ \\
	    \begin{subfigure}[b]{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-away}
	                \caption{Movement away from the sphere\\}
	                \label{subfig:1b-away}
	    \end{subfigure}
	    &
	    \begin{subfigure}[b]{0.45\textwidth}
	                \includegraphics[width=\textwidth]{1b-away2}
	                \caption{Movement farther away from the sphere}
	                \label{subfig:1b-away2}
	    \end{subfigure}
    \end{tabular}

    \begin{subfigure}{0.5\textwidth}
                \includegraphics[width=\textwidth]{1b-composite}
                \caption{The reflection is replaced with a reflection from another image (with a smaller sphere)}
                \label{subfig:1b-composite}
    \end{subfigure}
    \caption{A comparison of different types of forgeries in which the green cube is manipulated. Original image in Figure~\ref{1b-genuine}.}
	\label{forgery-comparison}
\end{figure}

@@

If applied to real-world examples, one problem that may arise is the lack of detail in the reflection, because it is likely that a spherical mirror occurring in the real world would be relatively small, and so the features of the reflection would be hard to distinguish. More research will likely be needed to determine how much detail is needed and how to enhance the reflections if necessary.

Finally, in order to be able to analyze most curved surfaces, methods will need to be developed to analyze reflections on other quadric surfaces, such as cylinders and cones. In these cases it would probably be necessary to develop a reliable method for estimating the normal, as these shapes are not regular as viewed from any angle like a sphere.
